Complex networks gradus ad parnassum

### 2015-05-05 article.tex
small enhancements

\section{\label{sec:models}Paradigmatic models}
\subsection{Small-world}
Characteristics, Measures, Generative models.
\subsection{Geographic}
Characteristics, Measures, Generative models.
\subsection{Scale-Free}
Characteristics, Measures, Generative models.
\subsection{Erd\"os-R\'enyi}
Characteristics, Measures, Generative models.
\subsection{Other recurrent network characteristics}
\section{\label{sec:inet}You-networks, I-networks}
\subsection{\label{sec:stabdiff}Stability and differentiation in human social networks}
\subsection{\label{sec:harn}Harnessing}
Software, ontologies, data, future forecast, next steps 
and future work, art, anthropological physics.

@@

\section{Complex networks measures}
Equation, definition and reference.

\section{Software data and media}
Equation, definition and reference.
\section{Related works}
\subsection{Articles}
\subsection{Books}
\section{Exercises}

>>>>

\section{\label{sec:models}Paradigmatic models}
\subsection{Small-world}
Characteristics, Measures, Generative models.
\subsection{Geographic}
Characteristics, Measures, Generative models.
\subsection{Scale-Free}
Characteristics, Measures, Generative models.
\subsection{Erd\"os-R\'enyi}
Characteristics, Measures, Generative models.
\subsection{Other recurrent network characteristics}
\section{\label{sec:inet}You-networks, I-networks}
\subsection{\label{sec:stabdiff}Stability and differentiation in human social networks}
\subsection{\label{sec:harn}Harnessing}
Procedures, ontologies, data, software, art, anthropological physics, 
future forecast, next steps and future work.

@@

\section{Measures}
Equation, definition and reference.

\section{Software, data and media}
\section{Related works}
\subsection{Articles}
\subsection{Books}
\section{Exercises}
Theory, real data analysis, anthropological physics experiments.
